2024 US Presidential Election Model

### 2024-10-20 paper/paper.qmd
committing text changes
commit changes to render
changes in latex for paper.qmd

## Model set-up
Define $y_i$ as the binary outcome variable indicating whether Donald Trump is predicted to win state $i$ (1 if Trump wins, 0 if Harris wins). The predictor variables are $ \beta_i $, the average percentage of polling support for Donald Trump in state $i$, and $ \gamma_i $, the average percentage of polling support for Kamala Harris in state $i$.

>>>>

## Model set-up
Define $y_i$ as the binary outcome variable indicating whether Donald Trump is predicted to win state $i$ (1 if Trump wins, 0 if Harris wins). The predictor variables are $\beta_i$, the average percentage of polling support for Donald Trump in state $i$, and $\gamma_i$, the average percentage of polling support for Kamala Harris in state $i$.
